Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-05-09 Documents/M1/realizableFermionicM1/sections/numerical.tex
Additional figure for packed beam problem

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figures/PackedBeam_Realizability}
   \caption{Plot of $\gamma(\vect{\cM})=(1-\cJ)\,\cJ-|\vect{\cH}|$ for various times in the packed beam problem: $t=0$ (cyan), $t=0.2$ (magenta), $t=0.4$ (blue), and $t=0.8$ (black).  Results obtained with the CB closure, which remain positive throughout the evolution, are plotted with solid lines, while results obtained with the Minerbo closure are plotted with dashed lines.}
  \label{fig:PackedBeam_Realizability}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_Realizability}
    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_RealizableDomain}
  \end{tabular}
   \caption{In the left panel, $\gamma(\vect{\cM})=(1-\cJ)\,\cJ-|\vect{\cH}|$ is plotted versus $x$ for various times in the packed beam problem: $t=0$ (cyan), $t=0.2$ (magenta), $t=0.4$ (blue), and $t=0.8$ (black).  Results obtained with the CB closure, which remain positive throughout the evolution, are plotted with solid lines, while results obtained with the Minerbo closure are plotted with dashed lines.  In the right panel, the moments are plotted in $(\cJ,\cH)$-space for the same times as in the left panel.  Results obtained with the CB and Minerbo closures are plotted in blue and magenta, respectively.  The solid black and red lines are contour where $(1-\cJ)\,\cJ=\cH$ and $\cJ=\cH$, respectively.}
  \label{fig:PackedBeam_Realizability}
\end{figure}
